### 2018-05-03 papers/synth/experiments.tex
vts example and conn

    plos1-dia[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 0.0492 & 0.0\\\hline
    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & \0.042 \\\hline
%[M=8, N=2, Q=2]    
% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
    mukund[3/4C] & 0.3809 & 0.0 & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
    node4[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 2.194 & 0.0\\\hline
    yeast-graph & 0.0 & 0.0 & 0.0 & 0.00 & 0.0 & 0.0 & 0.0  & 0.0 & 0.0 & 0.0 \\\hline
    mukund-comp & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs).}
  \label{tab:qf-grabh}
\end{table}

>>>>

    plos1-dia[3/4C] & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & UNSAT & 0.0492 & 0.0\\\hline
    plos2-dia [4C] & 2.206 & \#0.0414 & 0.0424 & \#0.0407 & 0.190 & 1.333[1 n] & 2.192 & 2.327[1n 9e] & 0.0499 & 0.042 \\\hline
%[M=8, N=2, Q=2]    
% n/A n/A activeN == UNSAT adding edge == UNSAT activeE == UNSAT presenceE == UNSAT
    mukund[3/4C] & 0.3809 & 185.06 & 0.3773 & 0.0 & 2.062 & 0.0 & !13.92/1.553 & 0.0 & 0.230 & 0.0 \\\hline
    node4[-] & 16.70 & 0.0 & 16.472 & 0.0 & UNSAT & UNSAT & UNSAT & UNSAT & 2.194 & 0.0\\\hline
    yeast-graph & 0.0 & 0.0 & 0.0 & 0.00 & 0.0 & 0.0 & 0.0  & 0.0 & 0.0 & 0.0 \\\hline
    mukund-comp & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0\\\hline
  \end{tabular}
  \caption{Run-times for searching for models (in secs).}
  \label{tab:qf-grabh}
\end{table}
